Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignments with the stellar disk

### 2019-07-18 Document/paper.tex
edit

\title[The shape of dark matter haloes at $z=0$ in Auriga]
{Dark matter halo shape at $z=0$ in the Auriga simulations: radial
  evolution and baryon disk alignments}
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\'a, Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies,
Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany.\\
}

>>>>

\title[The shape of dark matter haloes at $z=0$ in Auriga]
{Dark matter halo shape at $z=0$ in the Auriga simulations: radial
  evolution and alignments with the stellar disk}
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\'a, Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies,
Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany.\\
}
